Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-05 Paper/paperN.tex
spelling, add to abstract

\begin{abstract}
We explore two models for the unsupervised induction of semantic frames on a 
very large corpus of verb-subject-object triples. Our work is bade on previous 
research that has had success on smaller, more focused data sets. By encouraging 
verb sparsity with a Dirichlet prior, one can improve on the results of our 
baseline model. We give some analysis of the frames that the improved model 
discovers, and suggest areas for further development.

  Information in text can be represented by frames. A frame consists of a predicate with arguments. In this report we discuss two probabilistic latent variable models which are trained by resp. expectation maximization and Gibbs sampling, to induce frames from syntactic tri-grams of the form: verb, subject, object. The latent variable is the frame a verb belongs to. In practice, the models cluster verbs based on the occurrences of arguments they are encountered with. The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters). The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1. 
\end{abstract}

@@

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occuring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames. This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

A syntactic-ngram is a $k$-word rooted subtree of some sentence.
Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
books and labled with Penn Treebank part-of-speech tags Stanford-basic dependency 
labels \citep{ngrams2013}.
Each ngram also includes frequency counts by year.

@@

The $\alpha$ and $\beta$ hyperparameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem. We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$. The grid search builds, for each posible parameter set, a model which is evaluated on the cross validation set. The highest scoring model is tested with the test set. We ran grid search for model 0 on $50$ - $200$ frames, with steps of $50$, and $\alpha$ of $0.1, 0.5, 1, 1.5$, and $2$. The grid search for Model 1 was the the same, additionally testing $\beta$ across the same values as $\alpha$
\section{Results}
\label{results}

@@

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming anotherly &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\label{exframes}
\caption{Frame examples}
\end{table}

\section{Discussion}
As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much. But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are asigned to a frame. It is not clear why this happens, but this are still only experimental results.  Since there are 200 frames it is obvious that the coherency is so low. Other experiments have shown that it is possible to cluster with model 0 though.

The frames in table \ref{exframes} are frames induced by model 1 and are meaningfull in the sense that they consist of clusters of verbs that seem to have a similar meaning. Nontheless, in \textit{harming anotherly} there are verbs which would be better left out. They are assigned this frame though because they occurred in company of the same arguments often. The affection frame is remarkable since these are exactly opposites. This happens in some form in more frames though and can be explained by the fact that verbs with opposite meanings are used with the same arguments, this can be seen as a weakness of the model.

Furthermore auxilary verbs get mostly assigned a complete frame, i.e. they are the only verb assigned to a frame. Other verbs like \textit{(say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find)} also get assigned a complete frame. This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb by nouns it is encountered with, sort of meaningless. This is again a weakness of the model, but could possibly be diminished with more data.

\section{Future Work}
One big weakness of this project over the results of \citet{oconnor2013} is that 
we could not used document-level context to infer semantic information.
A possible direction of future research is to create models that take better 
advantage of the syntax-level context provided by syntactic ngrams. 
One easy way to do this would be to modify model 1 so that the argument 
vocabulary ranges over subject/object pairs instead of individual nouns.
or object.
More advanced models might take better advantage of the various kinds of arguments
in the verbargs dataset and their relation to one another.
For example, you could be glean some semantic information about the relationship between
verbs and prepositional objects by looking at the preposition that mediates them: 
That you ''swim \emph{in} a lake'' versus ``ice skate \emph{on} a lake'' 
indicates that the relationship between swimming and lakes is different from the one between
ice skating and lakes.

@@

\section*{Who did what}
We all tried to work as much as possible and neccesary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of gridsearch). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody.

>>>>

\begin{abstract}
  Semantic frames can be used to give a basic representation of a sentence's meaning. A frame consists of a predicate and its arguments. In this report we discuss two probabilistic latent variable models, which are trained by resp. expectation maximization and Gibbs sampling, to induce frames on syntactic tri-grams of the form verb, subject, object. The latent variable is the frame that the triple belongs to. In practice, the models cluster verbs based on the arguments with which they occur. The frames (or clusters of verbs) are measured for coherence (relative to each other) and correctness (relative to FrameNet clusters). By encouraging verb sparsity with a Dirichlet prior, the more sophisticated second model improves on our baseline. These results support similar findings in research where much smaller, more topically focused datasets were used. Finally, we give some analysis of the frames that our improved model discovers and suggest areas for further development.
\end{abstract}

@@

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximization on a simple co-occurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occurring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames. This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

A syntactic-ngram is a $k$-word rooted subtree of some sentence.
Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
books and labeled with Penn Treebank part-of-speech tags Stanford-basic dependency 
labels \citep{ngrams2013}.
Each ngram also includes frequency counts by year.

@@

The $\alpha$ and $\beta$ hyperparameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem. We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$. The grid search builds, for each possible parameter set, a model which is evaluated on the cross validation set. The highest scoring model is tested with the test set. We ran grid search for model 0 on $50$ - $200$ frames, with steps of $50$, and $\alpha$ of $0.1, 0.5, 1, 1.5$, and $2$. The grid search for Model 1 was the the same, additionally testing $\beta$ across the same values as $\alpha$
\section{Results}
\label{results}

@@

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming another &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\label{exframes}
\caption{Frame examples}
\end{table}

\section{Discussion}
As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much. But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame. It is not clear why this happens, but this are still only experimental results.  Since there are 200 frames it is obvious that the coherency is so low. Other experiments have shown that it is possible to cluster with model 0 though.

The frames in table \ref{exframes} are frames induced by model 1 and are meaningful in the sense that they consist of clusters of verbs that seem to have a similar meaning. Nonetheless, in \textit{harming another} there are verbs which would be better left out. They are assigned this frame though because they occurred in company of the same arguments often. The affection frame is remarkable since these are exactly opposites. This happens in some form in more frames though and can be explained by the fact that verbs with opposite meanings are used with the same arguments, this can be seen as a weakness of the model.

Furthermore auxiliary verbs get mostly assigned a complete frame, i.e. they are the only verb assigned to a frame. Other verbs like \textit{(say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find)} also get assigned a complete frame. This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb by nouns it is encountered with, sort of meaningless. This is again a weakness of the model, but could possibly be diminished with more data.

\section{Future Work}
One big weakness of this project over the results of \citet{oconnor2013} is that 
we could not used document-level context to infer semantic information.
A possible direction of future research is to create models that take better 
advantage of the syntax-level context provided by syntactic ngrams. 
One easy way to do this would be to modify model 1 so that the argument 
vocabulary ranges over subject/object pairs instead of individual nouns.
or object.
More advanced models might use detailed syntactic context to make more fine-grained
distinctions between syntactic contexts.
For example, you could be glean some semantic information about the relationship between
verbs and prepositional objects by looking at the preposition that mediates them: 
That you ``swim \emph{in} a lake'' versus ``ice skate \emph{on} a lake'' 
indicates that the relationship between swimming and lakes is different from the one between
ice skating and lakes.

More generally, VSO models don't take full advantage of the various kinds of argumens
in the verbargs dataset. 
As we have seen, only a fraction of verbs actually occur as part of a VSO subtree.
By considering only VSOs, we may introduce some bias in the frames that we can induce,
since frames with particular role configurationts (such as \emph{agent, patient}) may
lend themselves better to transitive verbs.

Finally, the models that we consider are essentially performing verb \emph{clustering}.
This is a good first step, but a more sophisticated version of semantic frame induction
would also be able to identify semantic \emph{roles}, and assign verb arguments to those
roles. 
That model 1 performs well on such a large, diverse dataset as Google syntactic ngrams is
encouraging since such a corpus would be necessary to induce semantic roles on top of frames.

@@

\section*{Who did what}
We all tried to work as much as possible and necessary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid search). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody.
